### 2021-01-29 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/methodology.tex
Add Related work, RDR pic and references

This is where, Ripple Down Rules (RDR) knowledge base, steps in. RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules. As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.

>>>>

This is where, Ripple Down Rules (RDR) knowledge base, steps in. RDR, by design, provides a safe and traceable data structure for creating, maintaining, and evolving knowledge, in the form of iterpretable rules \cite{compton1992ripple, richards2009two, kim2018rdr}. As \textbf{figRDR} shows, the RDR implementation, which serves as our schema map knowledge base, is very closely related to our schema matching algorithm.

### 2021-01-29 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/relatedwork.tex
intro 7
on ubuntu
change attribute Rpresenation diagrame
Algorithm set
Add Related work, RDR pic and references

\section*{Related Work}
Althubait et al. \cite{althubaiti2020combining} proposed an ontology expansion methodology that identifies and extracts new class from text articles using word embedding and machine learning techniques. The authors identified the similarity of tokens and phrases of the text articles with the exiting classes of the ontology. The target ontology is expanded with classes from text articles having greater similarity with that of already added classes. A similar word embedding technique was also used by Nozaki et al. \cite{nozaki2019semantic}, where the authors used instance based schema matching technique to identify the semantic similarity between two instances. The results of the study showed the possibility of detecting similar string attributes of different schemas. Yousfi et al. \cite{yousfi2020xmatcher} also utilized semantic base techniques and proposed xMatcher XML schemas matching approach. xMatcher transforms schemas into a set of words, followed by measuring words context, and relatedness score using WordNet. The terms from different schemas having similarities greater or equal to 0.8 are considered similar. 
Bylygin et al. \cite{bulygin2018combining} devised an ontology and schema matching approach by combining lexical and semantic similarity with machine learning approaches.  The authors used lexical and semantic measures as features and trained various machine learning algorithms including Naive Bayes, logistic regression, and gradient boosted tree. The result achieved showed that the combination of algorithms outperformed the single modal.

@@

>>>>

\section*{Related Work}
\label{relatedwork}
Althubait et al. \cite{althubaiti2020combining} proposed an ontology expansion methodology that identifies and extracts new class from text articles using word embedding and machine learning techniques. The authors identified the similarity of tokens and phrases of the text articles with the exiting classes of the ontology. The target ontology is expanded with classes from text articles having greater similarity with that of already added classes. A similar word embedding technique was also used by Nozaki et al. \cite{nozaki2019semantic}, where the authors used instance based schema matching technique to identify the semantic similarity between two instances. The results of the study showed the possibility of detecting similar string attributes of different schemas. Yousfi et al. \cite{yousfi2020xmatcher} also utilized semantic base techniques and proposed xMatcher XML schemas matching approach. xMatcher transforms schemas into a set of words, followed by measuring words context, and relatedness score using WordNet. The terms from different schemas having similarities greater or equal to 0.8 are considered similar. 
Bylygin et al. \cite{bulygin2018combining} devised an ontology and schema matching approach by combining lexical and semantic similarity with machine learning approaches.  The authors used lexical and semantic measures as features and trained various machine learning algorithms including Naive Bayes, logistic regression, and gradient boosted tree. The result achieved showed that the combination of algorithms outperformed the single modal.

@@

Xu et al. \cite{xu2003discovering} presented a framework for discovering indirect links besides direct links among schema elements. The indirect matches were detected for relations such as union, composition, decomposition, selection, and boolean. The indirect links are useful to handle concepts merge, split, generalization, and specialization. The matching techniques utilized in the study considered terminological relationships (word synonym and hypernym), structural characteristics, data-value characteristics, and expected data values. The experimental results revealed framework effectiveness by achieving more than 90\% precision and recall for direct and indirect link matching.
